The Chemistry Development Kit (CDK) v2.0: atom typing, depiction, molecular formulas, and substructure searching

### 2017-01-03 article.tex
OK, no names are broken up anymore
Updating the material to send in as the first submission was sent back
Pkg no longer used
No figures in the submission
For Software the Implementation and the Results is the same thing
JChemInf uses the Vancouver style
Address change
Whitehead Institute changed its official mailing address
Update John Mayfield Email
Hopefully somewhat less confusing - could also add a footnote. Previous email is still valid.

\NeedsTeXFormat{LaTeX2e}[1995/12/01]
\documentclass[10pt]{bmcart}
%\documentclass[twocolumn]{bmcart}% uncomment this for twocolumn layout and comment line below
%%% additional documentclass options:
%  [doublespacing]
%  [linenumbers]   - put the line numbers on margins

@@

%% Comment out before submission 
\usepackage[colorinlistoftodos,textsize=small]{todonotes}

@@

\author[
   addressref={um},                                 % ORCID: 0000-0001-7542-0286
   %corref={aff1},
   %noteref={n1},
   email={egon.willighagen@maastrichtuniversity.nl}
]{\inits{ELW}\fnm{Egon L} \snm{Willighagen}}
\author[
   addressref={nm},
   email={john.may@cantab.net}
]{\inits{JWM}\fnm{John W} \snm{Mayfield}}
\author[
   addressref={uppsala},
   email={jonathan.alvarsson@farmbio.uu.se}
]{\inits{JA}\fnm{Jonathan} \snm{Alvarsson}}
\author[
   addressref={uppsala},
   email={berg.arvid@gmail.com}
]{\inits{AB}\fnm{Arvid} \snm{Berg}}
\author[
   addressref={azg},                                % ORCID: 0000-0001-9491-4134
   email={Lars.A.Carlsson@astrazeneca.com}
]{\inits{LC}\fnm{Lars}~\snm{Carlsson}}
% \author[
%    addressref={jena},
%    email={kai.duehrkop@uni-jena.de}
% ]{\inits{KD}\fnm{Kai} \snm{Dührkop}}
\author[
   addressref={idea},
   email={jeliazkova.nina@gmail.com}
]{\inits{NJ}\fnm{Nina} \snm{Jeliazkova}}
\author[
   addressref={leicester},
   email={shk12@le.ac.uk}
]{\inits{SK}\fnm{Stefan} \snm{Kuhn}}
\author[
   addressref={wi_mit},                             % ORCID: 0000-0002-6940-3006
   email={pluskal@wi.mit.edu}
]{\inits{TP}\fnm{Tomáš}~\snm{Pluskal}}
\author[
   addressref={miquel},                             % ORCID: 0000-0002-4659-1446
   email={mrojas@qca.es}
]{\inits{MRJ}\fnm{Miquel}~\snm{Rojas-Chertó}}
\author[
   addressref={uppsala},
   email={ola.spjuth@farmbio.uu.se}
]{\inits{OS}\fnm{Ola} \snm{Spjuth}}
\author[
   addressref={gilleain},                           % ORCID: 0000-0002-8368-6954
   email={gilleain.torrance@gmail.com}
]{\inits{GT}\fnm{Gilleain} \snm{Torrance}}
\author[
   addressref={um},
   email={chris.evelo@maastrichtuniversity.nl}
]{\inits{CTE}\fnm{Chris~T}~\snm{Evelo}}
\author[
   addressref={nih},
   email={guhar@mail.nih.gov}
]{\inits{RG}\fnm{Rajarshi} \snm{Guha}}
\author[
   addressref={ebi},
   email={steinbeck@ebi.ac.uk}
]{\inits{CS}\fnm{Christoph}~\snm{Steinbeck}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Results and Discussion %%
%%
\section*{Results and Discussion}

@@

\bibliographystyle{bmc-mathphys}  % Style BST file
\bibliography{article}

@@

\begin{figure}[h!]
  \caption{\csentence{Relative storage of stereochemistry, the \textbf{type} and
    \textbf{focus} of stereochemsitry are fixed for a given
    stereocenter description but the \textbf{carriers} and
    \textbf{configuration} are relative.} 
  The multiple rows for each
  stereochemistry type are different internal representation that
  would be considered equivalent. In the tetrahedral types,
  hydrogens may be suppressed in a molecular graph so the
  \textbf{focus} is reused in the \textbf{carriers} list as a
  placeholder.}
\centering
\includegraphics{img/stereodesc_annotated.pdf}
\label{fig:stereodatastructure}
\end{figure}

\begin{figure}[h!]
  \caption{\csentence{The raw input files of CHEMBL23970 and CHEMBL444314 are displayed (ChEMBL 21).}
    Without perceiving the stereochemistry indicated by Haworth
    projection in CHEMBL23970, the database entries are incorrectly
    considered distinct. Down stream aggregation databases mirror this
    separation (PubChem CID 5280, CID 65119).}
    \centering
    \includegraphics{img/projections_annotated.pdf}
    \label{fig:stereoprojections}
\end{figure}

\begin{figure}[h!]
  \caption{\csentence{Integrated example showing the rendering and SMILES
      parsing functionality. Example from U.S. Patent \textbf{US 2014 231770 A1} para 287.}}
  \centering
  \includegraphics[width=\textwidth]{img/US20140231770A1_0287.pdf}
  \label{fig:depiction}
\end{figure}

\begin{figure}[h!]
  \caption{\csentence{{The improved structure diagram generation has improved
        code to solve overlap.}}
    The original SDG code used general heuristics (left) and the
    OverlapResolver would fine tune the layout to ensure atoms would not be placed
    at the same location (middle). The new SDG algorithm is able to
    make more rigorous changes, making the final output must more pleasing
    (right).}
    \includegraphics[width=\textwidth]{sdg.png}
    \label{fig:sdg}
\end{figure}

\begin{figure}[h!]
  \caption{\csentence{Structure diagram generation for structures with
      double bond and tetrahedral stereochemistry.}}
  \centering
  \includegraphics[width=0.3\textwidth]{sdg2.pdf}
  \label{fig:sdgstereo}
\end{figure}

\begin{figure}[h!]
  \caption{\csentence{Dependencies between CDK modules.}
    Visualization of the dependencies between CDK modules. For example,
    the cdk-core depends on the cdk-interfaces module. A few higher level
    modules have been left out: cdk-builder3dtools, cdk-legacy, and
    cdk-depict.}
  \centering
  \includegraphics[width=\textwidth]{cdkDeps.png}
  \label{fig:deps}
\end{figure}

\begin{figure}[h!]
  \caption{\csentence{Examples of Sgroups now captured by the CDK and
      encoded in molfiles and CXSMILES. a) Ethyl esterification fully
      expanded reaction. b) Using Sgroup abbreviations allows display
      short cuts and more compact depiction. c) An example of a
      structure repeat unit in \textit{DNA 5'-phosphate}
      (\textbf{CHEBI:4294})}}
  \includegraphics[width=\textwidth]{img/sgroups.pdf}
  \label{fig:sgroups}
\end{figure}

>>>>

\NeedsTeXFormat{LaTeX2e}[1995/12/01]
\documentclass[doublespacing]{bmcart}
%\documentclass[twocolumn]{bmcart}% uncomment this for twocolumn layout and comment line below
%%% additional documentclass options:
%  [doublespacing]
%  [linenumbers]   - put the line numbers on margins

@@

%% Comment out before submission 
%%\usepackage[colorinlistoftodos,textsize=small]{todonotes}

@@

\author[
   addressref={um},                                 % ORCID: 0000-0001-7542-0286
   %corref={aff1},
   %noteref={n1},
   email={egon.willighagen@maastrichtuniversity.nl}
]{\inits{ELW}\fnm{Egon L} \snm{Willighagen}}
\author[
   addressref={nm},
   email={john.mayfield@cantab.net}
]{\inits{JWM}\fnm{John W} \snm{Mayfield}}
\author[
   addressref={uppsala},
   email={jonathan.alvarsson@farmbio.uu.se}
]{\inits{JA}\fnm{Jonathan} \snm{Alvarsson}}
\author[
   addressref={uppsala},
   email={berg.arvid@gmail.com}
]{\inits{AB}\fnm{Arvid} \snm{Berg}}
\author[
   addressref={azg},                                % ORCID: 0000-0001-9491-4134
   email={Lars.A.Carlsson@astrazeneca.com}
]{\inits{LC}\fnm{Lars}~\snm{Carlsson}}
% \author[
%    addressref={jena},
%    email={kai.duehrkop@uni-jena.de}
% ]{\inits{KD}\fnm{Kai} \snm{Dührkop}}
\author[
   addressref={idea},
   email={jeliazkova.nina@gmail.com}
]{\inits{NJ}\fnm{Nina}~\snm{Jeliazkova}}
\author[
   addressref={leicester},
   email={shk12@le.ac.uk}
]{\inits{SK}\fnm{Stefan} \snm{Kuhn}}
\author[
   addressref={wi_mit},                             % ORCID: 0000-0002-6940-3006
   email={pluskal@wi.mit.edu}
]{\inits{TP}\fnm{Tomáš}~\snm{Pluskal}}
\author[
   addressref={miquel},                             % ORCID: 0000-0002-4659-1446
   email={mrojas@qca.es}
]{\inits{MRJ}\fnm{Miquel}~\snm{Rojas-Chertó}}
\author[
   addressref={uppsala},
   email={ola.spjuth@farmbio.uu.se}
]{\inits{OS}\fnm{Ola} \snm{Spjuth}}
\author[
   addressref={gilleain},                           % ORCID: 0000-0002-8368-6954
   email={gilleain.torrance@gmail.com}
]{\inits{GT}\fnm{Gilleain} \snm{Torrance}}
\author[
   addressref={um},
   email={chris.evelo@maastrichtuniversity.nl}
]{\inits{CTE}\fnm{Chris~T}~\snm{Evelo}}
\author[
   addressref={nih},
   email={guhar@mail.nih.gov}
]{\inits{RG}\fnm{Rajarshi} \snm{Guha}}
\author[
   addressref={ebi},
   email={steinbeck@ebi.ac.uk}
]{\inits{CS}\fnm{Christoph}~\snm{Steinbeck}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Results and Discussion %%
%%
\section*{Implementation and Results}

@@

\bibliographystyle{vancouver}  % Style BST file
\bibliography{article}

@@

\begin{figure}[h!]
  \caption{\csentence{Relative storage of stereochemistry, the \textbf{type} and
    \textbf{focus} of stereochemsitry are fixed for a given
    stereocenter description but the \textbf{carriers} and
    \textbf{configuration} are relative.} 
  The multiple rows for each
  stereochemistry type are different internal representation that
  would be considered equivalent. In the tetrahedral types,
  hydrogens may be suppressed in a molecular graph so the
  \textbf{focus} is reused in the \textbf{carriers} list as a
  placeholder.}
\centering
%\includegraphics{img/stereodesc_annotated.pdf}
\label{fig:stereodatastructure}
\end{figure}

\begin{figure}[h!]
  \caption{\csentence{The raw input files of CHEMBL23970 and CHEMBL444314 are displayed (ChEMBL 21).}
    Without perceiving the stereochemistry indicated by Haworth
    projection in CHEMBL23970, the database entries are incorrectly
    considered distinct. Down stream aggregation databases mirror this
    separation (PubChem CID 5280, CID 65119).}
    \centering
%    \includegraphics{img/projections_annotated.pdf}
    \label{fig:stereoprojections}
\end{figure}

\begin{figure}[h!]
  \caption{\csentence{Integrated example showing the rendering and SMILES
      parsing functionality. Example from U.S. Patent \textbf{US 2014 231770 A1} para 287.}}
  \centering
%  \includegraphics[width=\textwidth]{img/US20140231770A1_0287.pdf}
  \label{fig:depiction}
\end{figure}

\begin{figure}[h!]
  \caption{\csentence{{The improved structure diagram generation has improved
        code to solve overlap.}}
    The original SDG code used general heuristics (left) and the
    OverlapResolver would fine tune the layout to ensure atoms would not be placed
    at the same location (middle). The new SDG algorithm is able to
    make more rigorous changes, making the final output must more pleasing
    (right).}
%    \includegraphics[width=\textwidth]{sdg.png}
    \label{fig:sdg}
\end{figure}

\begin{figure}[h!]
  \caption{\csentence{Structure diagram generation for structures with
      double bond and tetrahedral stereochemistry.}}
  \centering
%  \includegraphics[width=0.3\textwidth]{sdg2.pdf}
  \label{fig:sdgstereo}
\end{figure}

\begin{figure}[h!]
  \caption{\csentence{Dependencies between CDK modules.}
    Visualization of the dependencies between CDK modules. For example,
    the cdk-core depends on the cdk-interfaces module. A few higher level
    modules have been left out: cdk-builder3dtools, cdk-legacy, and
    cdk-depict.}
  \centering
%  \includegraphics[width=\textwidth]{cdkDeps.png}
  \label{fig:deps}
\end{figure}

\begin{figure}[h!]
  \caption{\csentence{Examples of Sgroups now captured by the CDK and
      encoded in molfiles and CXSMILES. a) Ethyl esterification fully
      expanded reaction. b) Using Sgroup abbreviations allows display
      short cuts and more compact depiction. c) An example of a
      structure repeat unit in \textit{DNA 5'-phosphate}
      (\textbf{CHEBI:4294})}}
%  \includegraphics[width=\textwidth]{img/sgroups.pdf}
  \label{fig:sgroups}
\end{figure}
